---
title: "Unit7_Application"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(3221)

library(tidymodels)
library(kernlab)
library(tidyverse)
library(skimr)

```

## Question 1 
This question will use the OJ data set and an SVM with a polynomial kernel for classification.

a. Using skim, from the skimr package, quickly survey the data to determine types of data. 
     i. Are there any factors-levels that occur very infrequently?
    ii. Are there any predictors that are characters that need to be converted into factors?
   iii. Are there any missing values that will need to be accounted for?
   iv. Are there any index variables that need to be addressed?
   v. Are there any variables that have zero variability?
b. Split the data into a training set and a test set.
c. Fit a polynomial SVM to the training set using Purchase as the response and all the other variables as predictors (features). Tune via cost and degree.
d. Predict the values in the testing set and save the area under the ROC Curve.
e. Create a confusion matrix for your results.
f. Plot the ROC curve. 

### Answer

```{r Q1}
###The responses are reasonably balanced, so strata will likely not matter too much.
####Use your answers to a. to help with your recipe. (Don't be surprised if the data doesn't need any prep work)
###Make sure your response is a factor.

OJ_data <- ISLR::OJ
####

```


## Question 2 
This question will use the OJ data set and an SVM with a radial basis function kernel for classification.

a. Repeat items c-f from question 1, but this time use a radial kernel. Tune using just cost and rbf_sigma.
b. Compare your results to your results in Question 1. Which kernel performed the best?


### Answer

```{r Q2}


```

## Bonus
Plot the decision boundaries for Questions 1 and 2 with respect to PriceCM and PriceMM. 
You'll either have to figure out how to use slice in the kernlab plot (I'm still working on figuring it out myself). Or plot the boundary using a grid and predict.

### Answer

```{r Q2}


```